\documentclass[10pt,a4paper]{article}
\usepackage[margin=0.62in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.3em,itemsep=0pt,topsep=1pt,parsep=0pt,partopsep=0pt}
\renewcommand{\arraystretch}{1.08}
\urlstyle{same}

\newcommand{\sectiontitle}[1]{%
  \vspace{6pt}
  {\large\textbf{#1}}\par
  \vspace{2pt}
  \hrule
  \vspace{3pt}
}

\newcommand{\cventry}[3]{%
  \begin{tabularx}{\textwidth}{@{}Xr@{}}
    \textbf{#1} & \textit{#2} \\
    \multicolumn{2}{@{}X@{}}{#3}
  \end{tabularx}
  \par
}

\newcommand{\cvpubentry}[3]{%
  \begin{tabularx}{\textwidth}{@{}Xr@{}}
    {\textbf{\small #1}} & #2 \\
    #3 & \\
  \end{tabularx}
  \par
}

\begin{document}
\begin{center}
  {\LARGE\textbf{Kuan Wei Chen}}\\[3pt]
  \small
  No. 36, Ln. 510, Dadun 11th St., Nantun Dist., Taichung City 408021, Taiwan (R.O.C.)\\
  +886-976518289 \;|\;
  \href{mailto:elaping5691@gmail.com}{elaping5691@gmail.com} \;|\;
  \href{https://github.com/balaboom123}{github.com/balaboom123}
\end{center}

\sectiontitle{Education}
\cventry
  {National Central University, Taoyuan, Taiwan}
  {Starting Sep 2025}
  {Master in Computer Science, specialization in Artificial Intelligence}
\vspace{2pt}
\cventry
  {National Changhua University of Education, Changhua, Taiwan}
  {Sep 2021 -- Jun 2025}
  {Bachelor in Electrical Engineering, GPA 3.8/4.0 \;|\;
   \href{https://github.com/balaboom123/balaboom123/blob/main/certifications/NCUE_DD_S1052020.pdf}{Grad. Cert.}}

\sectiontitle{Experience}
\cventry
  {Project Assistant in AI Application Laboratory}
  {Jun 2025 -- Dec 2025}
  {{\href{https://github.com/balaboom123/balaboom123/blob/main/certifications/Project_Assistant_NCUE_AIAL.pdf}{Certificate}}}
\begin{itemize}
  \item Assisted in TEEP and IIPP projects, collaborating with 8 international interns.
  \item Contributed to ``Multi-biometric Authentication Systems'' and ``Action Recognition Systems''.
\end{itemize}

\sectiontitle{Publications}
\cvpubentry
  {STRLite: Lightweight Masked Autoencoders for Adaptable Scene Text Recognition}
  {\textit{\footnotesize IEEE ICCE}}
  {\href{https://github.com/balaboom123/STRLite}{GitHub}}
\begin{itemize}
  \item Co-first author; proposed a 6M-parameter MAE plus autoregressive STR pipeline for low-cost domain adaptation.
  \item Achieved 93.82\% weighted accuracy on six standard STR benchmarks and 81.03\% on U14M dataset.
\end{itemize}

\vspace{1pt}
\cvpubentry
  {Towards Compact Sign Language Translation: Frame Rate and Model Size Trade-offs}
  {\textit{\footnotesize IEEE ICCE}}
  {}
\begin{itemize}
  \item First author; built a 77M-parameter MMPose-to-T5-small gloss-free SLT pipeline.
  \item Showed that 12 fps cuts complexity by 75\% approximately with only a modest BLEU drop from 10.06 to 9.53.
\end{itemize}

\vspace{2pt}
\cvpubentry
  {\mbox{Two-step Authentication: Multi-biometric System Using Voice and Facial Recognition}}
  {\textit{\footnotesize IET~ICETA}}
  {\href{https://arxiv.org/abs/2601.06218}{arXiv} \;|\;
   \href{https://github.com/NCUE-EE-AIAL/Two-step-Authentication-Multi-biometric-System}{GitHub} \;|\;
   \href{https://github.com/balaboom123/balaboom123/blob/main/certifications/IET_ICETA_Certificate.pdf}{Certificate}}
\begin{itemize}
  \item First author; led a team of 2 international interns.
  \item Designed a ResNet-based voice verification architecture and utilize VGG16 for facial recognition in TensorFlow.
\end{itemize}

\sectiontitle{Projects}
\cventry
  {SignDATA: Data Pipeline for Sign Language Translation}
  {Python, Det, Pose, System Design}
  {\href{https://arxiv.org/abs/2604.20357}{arXiv} \;|\;
   \href{https://github.com/balaboom123/signdata-slt}{GitHub}}
\begin{itemize}
  \item First author; Open-source GitHub repo reached 100+ stars; Built a config-driven preprocessing toolkit that standardizes heterogeneous sign-language datasets into training-ready artifacts.
  \item designed pose and video recipes covering localization, clipping, cropping, landmark extraction, and export.
\end{itemize}

\sectiontitle{Skills}
\begin{tabularx}{\textwidth}{@{}p{0.30\textwidth}X@{}}
\textbf{Languages} & English (IELTS 6.5), Mandarin (native), Hokkien (native) \\
\textbf{Programming} & Python, C/C++ \\
\textbf{Libraries/Frameworks} & PyTorch, TensorFlow, Hugging Face, Scikit-learn, NumPy, Pandas \\
\textbf{Tools/Platforms} & Git, GitHub \\
\end{tabularx}

\sectiontitle{Awards and Certifications}
\cventry
  {Micro-Program in Green Energy Technology}
  {Electrical Engineering, NCUE}
  {}
\begin{itemize}
  \item Courses included ``Introductions to Green Energy Technology,'' ``Circuit Theory Experiments,'' ``Circuit Theory,'' and ``Special Topic for Industry.''
\end{itemize}

\vspace{2pt}
\cventry
  {Teaching Assistant -- Linear Algebra}
  {Electrical Engineering, NCUE}
  {\href{https://github.com/balaboom123/balaboom123/blob/main/certifications/NCUE_Teaching_Assistant.pdf}{Certificate}}
\begin{itemize}
  \item Created and delivered supplementary materials for 40+ students.
  \item Assisted with exam invigilation.
\end{itemize}

\vspace{2pt}
\cventry
  {Model United Nations Certifications}
  {2018--2019}
  {\href{https://github.com/balaboom123/balaboom123/blob/main/certifications/MUN/The\%207th\%20HSNU\%20Model\%20United\%20Nations\%20Conference\%20(2019).jpg}{HSNU MUN VII} \;|\;
   \href{https://github.com/balaboom123/balaboom123/blob/main/certifications/MUN/TCGSMUN\%20VII\%20Conference\%20(2019).jpg}{TCGSMUN VII} \;|\;
   \href{https://github.com/balaboom123/balaboom123/blob/main/certifications/MUN/Central\%20Taiwan\%20Model\%20United\%20Nations\%20IX\%20(2018).jpg}{Central Taiwan MUN IX} \;|\;
   \href{https://github.com/balaboom123/balaboom123/blob/main/certifications/MUN/Central\%20Taiwan\%20Model\%20United\%20Nations\%20XII\%20(2019).jpg}{Central Taiwan MUN XII}}

\end{document}
